SHINY APP

### 2016-08-06 final_paper/Shinyapp.Rmd
updated version

@@

rrr <- subset(stop_by, Hour = "7") %>% 
  group_by(Race) %>% 
  tally() 
rrr$Race<-as.factor(rrr$Race)

ggplot(rrr)+
  geom_bar(aes(x=Race, y = n),
           stat = "identity",
           fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF"))

@@

>>>>

             fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF")
```

@@

rrr <- subset(stop_by, Hour = "7") %>% 
  group_by(AgeRange) %>% 
  tally() 
rrr$Race<-as.factor(rrr$Race)

ggplot(rrr)+
  geom_bar(aes(x=AgeRange, y = n),
           stat = "identity")

ggplot(rrr)+
  geom_bar(aes(x=AgeRange, y = n),
           stat = "identity",
           fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF"))

@@

```{r}
subset(stop_by, Hour = "7") %>% 
    group_by(Agerange) %>% 
    tally()

  test <- subset(stop_by, Hour = input$hour) %>% 
    group_by(input$dataset) %>% 
    tally()

  test$Race<-as.factor(test$Race)

     sidebarPanel(
      sliderInput('hour',
                  'HOUR: ',
                  0, 24, value=7,
                  animate = T),

```{r}
ggmap(berkMap) +
  stat_density2d(aes(x = long, y = lat, fill = ..level.., alpha = ..level..),
    bins = I(5), geom = "polygon", data = mergedf ) +
  scale_fill_gradient2( "Stop Density",
    low = "white", mid = "orange", high = "red", midpoint = 25) +
  labs(x = "Longitude", y = "Latitude") + facet_wrap(~ AgeRange) +
  scale_alpha(range = c(.2, .55), guide = FALSE) +
  ggtitle("BPD Stop Contour Map of Berkeley by Age Range") +
  guides(fill = guide_colorbar(barwidth = 1.5, barheight = 10))
